An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
edit algorithm
lalala

The first component learns rules over typed templates and \emph{untyped specifications}, 
which must hold over multiple parts of a configuration file. An example of an
untyped specification is the ordering or missing entry constraint.

\para{A strawman solution.}
We first present a strawman solution (employed by
previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
a set of correct configuration files as a learning set, 
from which it is possible to derive rules 
that must hold with absolute certainty. 
In practice, however, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

    \State $R = \{\}$ // rule set
    \State $\Pi$ // probabilities associated with rule set
    \For{each file $F$ in $C$}
      \For{each $\tau \in \theta$}
        \State $Q = filter(F,\tau)$ 
        \State // $Q$ contains entries in $F$ with $\tau$ in type list
        \State $RM$ contains entries in remove set
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
                        \Else 
                        \State $CR = \textrm{constructTRules}(e, \tau, Q \backslash RM)$
                        \State $R = R  \cup CR$
                        \State For each $r \in CR$, update $\Pi$ 
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
      \For{each $u \in U$}
        \State $RM$ contains entries in remove set
        \For{each entry $e$ in $F$}
               \If{$g(e)$ is false}
                        \State continue to next entry
                        \Else 
                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
                        \State $R = R  \cup CR$
                        \State For each $r \in CR$, update $\Pi$ 
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
    \EndFor
    \EndFor
    \State return $(\Pi,R)$
  \end{algorithmic}
\end{algorithm}

>>>>

The first component learns two types of rules: rules that are inferred  using typed templates and 
rules which we call \emph{untyped specifications}. Those are rules
that must hold over multiple parts of a configuration file. An example of an
untyped specification is the ordering or missing entry constraint.

\para{A strawman solution.}
We first present a strawman solution (employed by
previous work~\cite{santolucitoCAV}) that uses 
a set of correct configuration files as a learning set, 
from which it is possible to derive rules 
that must hold with absolute certainty. 
In practice, however, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

    \State $R = \{\}$ // rule set
    \State $\Pi$ // probabilities associated with rule set
    \For{each file $F$ in $C$}
      \State Initialize $opt$ flag.
      \For{each $z \in \theta \cup U$}
        \If{$z$ is a type} $opt = 1$
        \ElsIf{$z$ is an untyped spec} $opt = 0$
        \EndIf
        \State $Q$ contains candidate entries to pass on %
        \State $RM$ contains entries in remove set
        \If{opt}
          \State $Q = filter(F,\tau)$ 
          \State // Q contains $F$ entries with $\tau$ in type list
          \Else{$\enspace Q = F$}
        \EndIf
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
               \Else
                        \State $Y = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
                        \State $R = R  \cup Y$
                        \State For each $r \in Y$, update $\Pi$ 
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
    \EndFor
%      \For{each $u \in U$}
%        \State $RM$ contains entries in remove set
%        \For{each entry $e$ in $F$}
%               \If{$g(e)$ is false}
%                        \State continue to next entry
%                        \Else 
%                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
%                        \State $R = R  \cup CR$
%                        \State For each $r \in CR$, update $\Pi$ 
%               \EndIf
%               \State $RM = RM \cup e$
%        \EndFor
%     \EndFor
%    \EndFor
    \State return $(\Pi,R)$
  \end{algorithmic}
\end{algorithm}
